Analyzing the Privacy Paradox Using a Nationally Representative Three-Wave Panel Study

### 2020-12-18 manuscript.RmD
- updated for revision

```{r load-packs, include=F}
# Load and install packages
# devtools::install_github("tdienlin/td@v.0.0.2.5")  # uncomment to install
# devtools::install_github("benmarwick/wordcountaddin", type = "source", dependencies = TRUE) # uncomment to install
packages <- c("broman", "GGally", "kableExtra", "knitr", "lavaan", "magrittr", "papaja"
             , "psych", "pwr", "td", "tidyverse", "semTools", "scales")
invisible(lapply(packages, library, character.only = T))

@@

@@

Evidence of within-person longitudinal effects is still missing. 
Although we found significant within-person correlations at T1, they were absent across the 6-month intervals.
Together, this suggests that longitudinal effects might exist, but that they take place on a different time interval.
Future research could hence probe different intervals.
For theoretical reasons (e.g., due to availability heuristics), it is plausible to use short intervals;
for statistical reasons (e.g., because of the high stability of privacy concerns), it would also make sense to test longer intervals  [@dormannOptimalTimeLags2015].

Although we argue that in most circumstances privacy concerns and behavior should correlate modestly, the exact extent depends on a many boundary conditions.
Future research should hence explicitly analyze different contexts [@nissenbaumPrivacyContextTechnology2010] and situations [@masurSituationalPrivacySelfdisclosure2018]. 
Building on @kokolakisPrivacyAttitudesPrivacy2017, we suggest to analyze the following boundary conditions:

 - Context (e.g., professional, social, commercial, or health-related);
 - Situation (e.g., new, habitualized, or unexpected);
 - Mood (e.g., positive vs. negative);
 - Extent of control (high vs. low);
 - Type of information processing applied (implicit, heuristic, or peripheral vs. explicit, analytic, or central);
 - Existence of bias (e.g., overconfidence, optimism, comparative optimism, or hyperbolic discounting);
 - Type of information (e.g., sensitive vs. superficial, biographic, or person-related);
 - Benefit immediacy and risk diffusion (high vs. low).

@@

 - Analysis design (e.g., theoretical, experimental, questionnaire-based, interview-based, or anecdotal);
 - Quality of measurement (high vs. low; low quality less likely to detect statistical significance);
 - Sample size (small vs. large; small samples less likely to detect statistical significance);
 - Statistical analysis (e.g., SEM vs. Regression; analyses without error control less likely to find statistical significance);
 - Operationalization (e.g., concerns vs. risk perceptions vs. behavioral attitudes; the more specific, the stronger the relation).

>>>>

```{r load-packs, include=F}
# Load and install packages
# devtools::install_github("tdienlin/td@v.0.0.2.5")  # uncomment to install
# devtools::install_github("benmarwick/wordcountaddin", type = "source", dependencies = TRUE) # uncomment to install
# devtools::install_github("crsh/papaja")  # uncomment to install
# devtools::install_github("cran/MissMech")
packages <- c("broman", "GGally", "kableExtra", "knitr", "lavaan", "magrittr", "papaja"
             , "psych", "pwr", "td", "tidyverse", "semTools", "scales")
invisible(lapply(packages, library, character.only = T))

@@

In what follows we hence investigate the two concepts of (a) concerns about online privacy and (b) online information sharing, aiming to investigate how they relate conceptually. In doing so, we adopt and focus on the perspective of individual people.

@@

Next, evidence of within-person longitudinal effects is still missing. 
Although we found significant within-person correlations at T1, they were absent across the 6-month intervals.
Together, this suggests that longitudinal effects might exist, but that they take place on a different time interval.
Future research could hence probe different intervals.
For theoretical reasons (e.g., due to availability heuristics), it is plausible to use short intervals;
for statistical reasons (e.g., because of the high stability of privacy concerns), it would also make sense to test longer intervals  [@dormannOptimalTimeLags2015].

In general, we emphasize that our findings should not be overgeneralized. 
They are conditional on the data we collected, the methods we applied, and the theoretical perspectives we adopted. 
We stress that analyzing the privacy paradox in other contexts using alternative approaches will likely lead to different results.
Although we argue that in most circumstances privacy concerns and behavior should correlate modestly, the exact extent depends on a many boundary conditions.
Future research should hence explicitly analyze different contexts [@nissenbaumPrivacyContextTechnology2010] and situations [@masurSituationalPrivacySelfdisclosure2018]. 
Building on @kokolakisPrivacyAttitudesPrivacy2017, we suggest to analyze the following boundary conditions:

 - Context (e.g., professional, social, commercial, or health-related);
 - Situation (e.g., new, habitualized, or unexpected);
 - Mood (e.g., positive vs. negative);
 - Extent of control (high vs. low);
 - Type of information processing applied (implicit, heuristic, or peripheral vs. explicit, analytic, or central);
 - Existence of bias (e.g., overconfidence, optimism, comparative optimism, or hyperbolic discounting);
 - Type of information (e.g., sensitive vs. superficial, biographic, or person-related);
 - Benefit immediacy and risk diffusion (high vs. low);
 - Object of investigation (e.g., individual people, interactions between people, developmental perspectives, critical incidents, societal structures, or historical developments).

@@

 - Analysis design and perspective (e.g., theoretical, experimental, questionnaire-based, interview-based, ethnographic, or computational);
 - Quality of measurement (high vs. low; low quality less likely to detect statistical significance);
 - Sample size (small vs. large; small samples less likely to detect statistical significance);
 - Statistical analysis (e.g., SEM vs. Regression; analyses without error control less likely to find statistical significance);
 - Operationalization (e.g., concerns vs. risk perceptions vs. behavioral attitudes; the more specific, the stronger the relation).
